Hydra Battles and Cie

### 2021-08-22 doc/part-hydras.tex
conversion to Alectryon (chapter 5, more than half done)

\begin{Coqsrc}
Lemma m_ge_0 alpha:  nf alpha -> alpha t1<= m (iota alpha).
\end{Coqsrc}

@@

\begin{Coqsrc}
  Definition big_h := iota mu.
  Definition beta_h := m big_h.
  Definition small_h := iota beta_h.
\end{Coqsrc}

From Lemma \texttt{m\_ge\_0} we infer the following inequality :

\begin{Coqsrc}
    Corollary m_ge_generic : m big_h t1<= m small_h.
 \end{Coqsrc}

@@

  Context (mu: T1)
          (Hmu: nf mu)
          (m : Hydra -> T1)
          (Var : Hvariant  T1_wf free m)
          (Hy : BoundedVariant Var mu).
  \end{Coqsrc}

@@

\begin{Coqsrc}
Lemma m_ge : m big_h t1<= m small_h.
  Proof.
    apply m_ge_generic.
   (* ... *)
\end{Coqsrc}

\item From the hypothesis \texttt{m\_bounded}, we have \texttt{m big\_h t1< mu}
\item By Lemma \texttt{LT\_to\_battle}, we get a (free) battle from
\texttt{big\_h = iota mu} to \texttt{small\_h = iota (m big\_h)}.

\begin{Coqsrc}
  Lemma  big_to_small : big_h  -+-> small_h.
\end{Coqsrc}
\item From the hypotheses on $m$, we infer:

\begin{Coqsrc}
Lemma m_lt : m small_h t1< m big_h.
\end{Coqsrc}

\item From lemmas \texttt{m\_ge} and \texttt{m\_lt}, and the irreflexivity of $<$, we get a contradiction.

  \begin{Coqsrc}
Theorem Impossibility_free : False.

@@

\begin{Coqsrc}
Check Impossibility_free.
\end{Coqsrc}

\begin{Coqanswer}
Impossibility_free
     : forall (mu : T1) (m : Hydra -> T1) (Var : Hvariant T1_wf free m),
       BoundedVariant Var mu -> False
\end{Coqanswer}
%%% ICI

>>>>

\input{movies/snippets/Epsilon0_Needed_Generic/mGe0}

@@

\input{movies/snippets/Epsilon0_Needed_Generic/mGeGeneric}

@@

\input{movies/snippets/Epsilon0_Needed_Free/theContext}

@@

\input{movies/snippets/Epsilon0_Needed_Free/mGe}

\item From the hypothesis \texttt{Hy}, we have \texttt{m big\_h t1< mu}
\item By Lemma \texttt{LT\_to\_round\_plus}, we get a (free) battle from
\texttt{big\_h = iota mu} to \texttt{small\_h = iota (m big\_h)}.

\input{movies/snippets/Epsilon0_Needed_Free/bigToSmall}

\item From the hypotheses on $m$, we infer:
\input{movies/snippets/Epsilon0_Needed_Free/mLt}

\item From lemmas \texttt{m\_ge} and \texttt{m\_lt}, and the irreflexivity of $<$, we get a contradiction. 
\input{movies/snippets/Epsilon0_Needed_Free/ImpossibilityFree}

@@

\input{movies/snippets/Epsilon0_Needed_Free/CheckDemo}
